\begin{abstract}
Nowadays, Android testing is becoming more and more challenging due to the notorious fragmentation issues and the complexity of usage scenarios. Therefore, crowdsourcing testing came into being. However, because of the unsupervised testing process and the lack of threshold for crowdsourcing workers, the quality of crowdsourcing testing needs to be improved urgently. According to the idea of collective intelligence, this article proposes a tool named TGCT, which combined with crowdsourcing testing and automated testing. This tool contains three main usages. Firstly, This tool will take the exception triggered by the automated test as the test task, guiding the crowdsourcing workers to verify the exception in different devices and environments. Secondly, according to the static analysis of the program source code, this tool finds the uncovered test case and use them to guide the crowdsourcing workers to explore new exceptions. Thirdly, based on the item-based collaborative filtering algorithm, TGCT implements a recommendation system for test cases to allocate different testing tasks to different crowdsourcing workers. Further, we carried out a crowdsourcing test comparison experiment in three real Android applications, and analyzed the test results from the perspective of crowdsourcing test coverage and efficiency, proving that the mechanism proposed in this paper can effectively improve the quality of crowdsourcing test. The demo video can be found at www.xxx.com.
\end{abstract} 