\section{Conclusion}
Crowdsourcing is gradually applied to the field of software testing with its low cost, high return and fast iteration. However, traditional crowdsourcing testing has some problems such as crowdsourcing workers being unable to collaborate because of their pool professional skill. Therefore, effectively managing the process of crowdsourcing testing and the guidance for crowdsourcing workers is signficant.
This paper proposes an improved crowdsourcing testing mechanism.This mechanism is composed of mobile application automation testing and static source code analysis, which help to guide crowdsourcing workers to verify the exceptions triggered by automated tests in different environments and explore new exceptions that found by static source code analysis. On the one hand, TGCT build the program GUI model based on automated testing and static analysis and improve the task decomposition from a more professional perspective. On the other hand, TGCT collects the historical test behavior of crowdsourcing workers, implements a collaborative test task recommendation system to optimizes resource allocation and improves overall test efficiency. When the crowdsourcing worker selects a test task, the TGCT calculates the shortest path from the current window to the start window of the test task based on the GUI model, and obtains the sequence of events corresponding to the window jump. In combination with the screenshot annotation and the text information. TGCT helps notify the crowdsourcing workers corresponding test events. We experimented on the three applications of "Jiandou", "QQ Video" and "Record".
From three aspects: test efficiency, abnormal coverage and feedback from crowdsourcing workers to test task recommendation system, it is proved that our guidance mechanism can effectively improve the quality of crowdsourcing test.